The three experiments presented in this paper are conceptual
replications of 3 previously run studies, an account of which is
available in the permanent online repository holding supplementary
material for this article\footnote{\url{https://osf.io/8fz4m/?view_only=ff5859d3f33b485d95254395f95a52dc}}.
The current studies have an increased sample size, and were conducted
concurrently on the same general population, to ensure that their
results could be compared directly. The stimuli were also redesigned to
read more naturally, and filler stimuli were included to ensure
replicability\footnote{To note, in the original studies, participants
  saw each condition no more than once. We suspect that in crowdsourced
  studies, when participants can be exposed to a very small number of
  stimuli without repeating any experimental conditions, fillers may at
  times be unnecessary, provided there is sufficient difference between
  experimental conditions -- and in fact, possibly detrimental to
  performance, if an increased number of items, and/or longer experiment
  duration, causes participants to read less closely for meaning.}.

The following experiments were run using the same interface, and on the
same population of Amazon Mechanical Turk workers, in small rotating
batches (of 9, or less): a batch of 9 participants completed the first
experiment, after which the second experiment was scripted to go live
until it was completed by 9 participants, and so forth. The only
difference between the 3 experiments was the manipulation of prosody or
discourse markers. Running them concurrently and on the same population
therefore allows us to directly compare their results. All workers who
participated in an experiment were automatically disqualified from
participating in any future batches; i.e., no participant took part in
more than one experiment or batch.

The number of eligible participants (n=2100) was predetermined through a
simulation power analysis \citep[adapted from][]{Arnold2011}: all predicted higher-order interactions, assuming effect
sizes determined by the results of the experiments we are replicating,
were detectable at \(>\) .80. The \texttt{R} code and a plot for the
power analysis can be found in the supplementary materials\footnote{\url{https://osf.io/84jdp/?view_only=ff5859d3f33b485d95254395f95a52dc}}.