\footnotesize

\begin{longtable}[c]{p{0.015\textwidth}||p{0.21\textwidth}|p{0.33\textwidth}|p{0.13\textwidth}|p{0.21\textwidth}}
&\centering\textsc{Common Ground}&\centering&&\multicolumn{1}{c}{\textsc{Utterance}} \\
\hline
\hline
\multirow{2}{*}{1} & John often goes to the grocery store around the corner from his apartment. $^{ordinary}$ & \multirow{2}{\linewidth}{Recently, he came home from the store with groceries.  When he came in, he saw his roommate Susan in the hallway, and started talking to her about his trip to the store.  As he went to the kitchen to put his groceries away, Susan went to the living room, where their roommate Peter was watching TV.} & \multirow{2}{\linewidth}{Susan said to Peter:} & ``John just came back from the grocery store. He paid the cashier.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & John is typically broke, and doesn't usually pay when he goes to the grocery store. $^{wonky}$ &  &  & ``John just came back from the grocery store. He got some apples.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{2} & Mary is a journalist who often goes to restaurants after her interviews. $^{ordinary}$ & \multirow{2}{\linewidth}{Yesterday, she went to a popular Chinese place.  As she was leaving, she ran into her friend David, and they started talking about the restaurant.  After they parted, David continued on his way when he suddenly ran into Sally, a mutual friend of him and Mary.} & \multirow{2}{\linewidth}{David said to Sally:} & ``I ran into Mary leaving that Chinese place. She ate there.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Mary is a journalist who often interviews restaurant waiters, but doesn't like eating out. $^{wonky}$ &  &  & ``I ran into Mary leaving that Chinese place. She got to see their kitchen.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{3} & Jim lives in a shared apartment, where it's his job to feed the dog in the evenings. $^{ordinary}$ & \multirow{2}{\linewidth}{The other day he was feeding the dog some canned food, as his roommate Lucy came into the kitchen, and made herself a snack while chatting with him.  Later in the evening, she settled down to watch TV alone with their roommate Carl.} & \multirow{2}{\linewidth}{Lucy said to Carl:} & ``Jim was feeding the dog earlier. He threw the can away.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Jim lives in a shared apartment with his dog, but can't seem to keep the common areas clean. $^{wonky}$ &  &  & ``Jim was feeding the dog earlier. He had to add some medication to the food.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{4} & Jane takes the subway all the time to get around the city. $^{ordinary}$ & \multirow{2}{\linewidth}{Today she was entering a subway station when she ran into her friend Don, and they took the train together as they were heading in the same direction.  Later that day, Don ran into Beth, Jane's sister, on the street.} & \multirow{2}{\linewidth}{Don said to Beth:} & ``I took a train with Jane today. She bought a subway ticket.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Jane takes the subway all the time to get around the city, but rarely pays for her rides. $^{wonky}$ &  &  & ``I took a train with Jane today. She almost fell off the platform.'' $^{non-habitual}$ \\
\hline
\end{longtable}

\pagebreak

\begin{longtable}[c]{p{0.015\textwidth}||p{0.21\textwidth}|p{0.33\textwidth}|p{0.13\textwidth}|p{0.21\textwidth}}
&\centering\textsc{Common Ground}&\centering&&\multicolumn{1}{c}{\textsc{Utterance}} \\
\hline
\hline
\multirow{2}{*}{5} & Rick prefers to go to the local gas station to fuel up, though they overcharge him. $^{ordinary}$ & \multirow{2}{\linewidth}{Yesterday he was fueling up there when he saw his friend Annie.  They talked until he was finished, then said goodbye.  After he was gone Annie went inside to buy some cigarettes, and ran into Sean, a mutual friend of theirs.} & \multirow{2}{\linewidth}{Annie said to Sean:} & ``Rick just fueled up here. He closed the fuel cap.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Rick often doesn't pay attention to what he's doing when he fuels up at the local gas station. $^{wonky}$ &  &  & ``Rick just fueled up here. He got some discounted gas.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{6} & Lisa likes to go swimming at a nearby pool after work. $^{ordinary}$ & \multirow{2}{\linewidth}{A couple days ago she was at the pool when she saw Harvey, another regular member, and they stopped to chat.  After Harvey changed and went out into the pool area, he ran into Jen, another swimmer and a friend of Lisa's.} & \multirow{2}{\linewidth}{Harvey said to Jen:} & ``Lisa's here to swim, too. She brought her swimsuit.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Lisa likes to go swimming regularly, but often forgets to bring the things she needs. $^{wonky}$ &  &  & ``Lisa's here to swim, too. She came with her children.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{7} & Brian takes the train most mornings, though the commute takes a long time. $^{ordinary}$ & \multirow{2}{\linewidth}{Last week when he was getting on the train, he ran into his old colleague Rachel, and they chatted until Brian got off.  When Rachel got to work, she saw Oliver, who also used to work with Brian.} & \multirow{2}{\linewidth}{Rachel said to Oliver:} & ``I saw Brian on the train this morning. He got off at his stop.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Brian takes the train most mornings, though he has a terrible habit of getting distracted and missing his stop. $^{wonky}$ &  &  & ``I saw Brian on the train this morning. He was running late to work.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{8} & Laura works as a software engineer at a large company. $^{ordinary}$ & \multirow{2}{\linewidth}{A couple of days ago she was getting ready to leave for work together with her husband Dustin.  After they both left the house, he ran to catch his bus, and met up with Courtney, an acquaintance who took the same bus with him every day.} & \multirow{2}{\linewidth}{Dustin said to Courtney:} & ``Laura was just getting ready for work with me. She grabbed her house keys.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Laura works as a software engineer at a large company, but is scatter-brained in everyday life. $^{wonky}$ &  &  & ``Laura was just getting ready for work with me. She put on several layers of clothing.'' $^{non-habitual}$ \\
\hline
\end{longtable}

\pagebreak

\begin{longtable}[c]{p{0.015\textwidth}||p{0.21\textwidth}|p{0.33\textwidth}|p{0.13\textwidth}|p{0.21\textwidth}}
&\centering\textsc{Common Ground}&\centering&&\multicolumn{1}{c}{\textsc{Utterance}} \\
\hline
\hline
\multirow{2}{*}{9} & Bruce goes to his local medical practice every few years. $^{ordinary}$ & \multirow{2}{\linewidth}{Yesterday after leaving the practice he ran into his friend Sarah on the street, and they stopped to catch up.  After they parted, Sarah walked on and soon saw Bruce's brother Drake on the street.  She stopped to say Hi.} & \multirow{2}{\linewidth}{Sarah said to Drake:} & ``Bruce was just leaving the medical practice. He got examined by the doctor.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Bruce goes to his local medical practice every few years, but usually only sees the nurse. $^{wonky}$ &  &  & ``Bruce was just leaving the medical practice. He was wearing a heart rate monitor.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{10} & Olivia has beautiful hair, and pays a lot of attention to it. $^{ordinary}$ & \multirow{2}{\linewidth}{Today, when she was leaving the bathroom after showering, she ran into her roommate and best friend Thomas.  She talked to him briefly about her hair, as she tends to do.  Later that day, when their housemate Jill came home, she and Thomas started talking about Olivia.} & \multirow{2}{\linewidth}{Thomas said to Jill:} & ``Olivia was talking to me about washing her hair. She used shampoo.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Olivia has beautiful hair, although she uses a cleansing conditioner only. $^{wonky}$ &  &  & ``Olivia was talking to me about washing her hair. She found some split ends.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{11} & Jared takes skydiving courses at the local airfield, when he has free time. $^{ordinary}$ & \multirow{2}{\linewidth}{Last week he was at the skydiving center, with his friend Stella in the same group as him.  They spent the day together, and when Stella went home in the evening, she texted Jared's brother Don, who was also a good friend of hers.} & \multirow{2}{\linewidth}{Stella said to Don:} & ``Jared was in the skydiving course today. He jumped out of the plane.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Jared takes skydiving courses at the local airfield, although he is still terrified of heights. $^{wonky}$ &  &  & ``Jared was in the skydiving course today. He was the first to jump.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{12} & Amy enjoys writing letters to people she is close to, especially around holidays. $^{ordinary}$ & \multirow{2}{\linewidth}{About two days ago, she wrote a letter to her cousin Michelle, and today she talked about it with her brother Steve.  In the evening, Steve got a call from Michelle, and they started talking about family.} & \multirow{2}{\linewidth}{Steve said to Michelle:} & ``Amy wrote you a letter. She mailed it.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Amy enjoys writing letters to people she is close to, but prefers to keep them to herself rather than mailing them. $^{wonky}$ &  &  & ``Amy wrote you a letter. She used really expensive stationery.'' $^{non-habitual}$ \\
\hline
\end{longtable}

\pagebreak

\begin{longtable}[c]{p{0.015\textwidth}||p{0.21\textwidth}|p{0.33\textwidth}|p{0.13\textwidth}|p{0.21\textwidth}}
&\centering\textsc{Common Ground}&\centering&&\multicolumn{1}{c}{\textsc{Utterance}} \\
\hline
\hline
\multirow{2}{*}{13} & Adam usually takes the bus to work, as the stop is a few blocks from his house. $^{ordinary}$ & \multirow{2}{\linewidth}{Last week, after he got off the bus, he ran into Virginia, his ex-girlfriend.  They stopped for a little while to catch up.} & \multirow{2}{\linewidth}{Adam said to Virginia:} & ``I took the bus this morning. I walked to the bus stop.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Adam usually takes the bus to work, but bikes to the stop although it's only a few blocks from his house. $^{wonky}$ &  &  & ``I took the bus this morning. I barely had room to stand.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{14} & Esther often goes along with her friends when they go clothes shopping, as it's something she also enjoys. $^{ordinary}$ & \multirow{2}{\linewidth}{Today, when she was walking out of a mall after spending time with her friends, she ran into George, another old friend of hers.  They decided to catch up while walking to the bus stop.} & \multirow{2}{\linewidth}{Esther said to George:} & ``I was out clothes shopping. I tried something on.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Esther often goes along with her friends when they go clothes shopping, although it bores her, and she just reads as they browse. $^{wonky}$ &  &  & ``I was out clothes shopping. I came across a big sale.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{15} & Nick enjoys making pasta dishes for his roommates, as it's an easy way to contribute to the household. $^{ordinary}$ & \multirow{2}{\linewidth}{Yesterday he was preparing pasta in the kitchen, to sit in the fridge until a party tomorrow.  When he was done and cleaning up, his roommate Clara came into the kitchen, and they started talking about his dish.} & \multirow{2}{\linewidth}{Nick said to Clara:} & ``I made some pasta for the meal. I boiled it in water.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Nick enjoys making pasta dishes for his roommates, but prefers to bake fresh pasta that doesn't need to be pre-boiled. $^{wonky}$ &  &  & ``I made some pasta for the meal. I added some vegetables.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{16} & Grace enjoys baking, as it's a great way to make new friends. $^{ordinary}$ & \multirow{2}{\linewidth}{A few days ago she was baking a cake in her kitchen.  After she had put it in the oven, her roommate Kyle came into the kitchen to make a salad for himself.  They started chatting about food.} & \multirow{2}{\linewidth}{Grace said to Kyle:} & ``I'm baking a cake right now. I preheated the oven.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Grace enjoys baking, although she's terrible at following basic directions in recipes. $^{wonky}$ &  &  & ``I'm baking a cake right now. I added chocolate chips to the recipe.'' $^{non-habitual}$ \\
\hline
\end{longtable}

\pagebreak

\begin{longtable}[c]{p{0.015\textwidth}||p{0.21\textwidth}|p{0.33\textwidth}|p{0.13\textwidth}|p{0.21\textwidth}}
&\centering\textsc{Common Ground}&\centering&&\multicolumn{1}{c}{\textsc{Utterance}} \\
\hline
\hline
\multirow{2}{*}{17} & Greg frequently travels by air, to see family and attend conferences. $^{ordinary}$ & \multirow{2}{\linewidth}{Last week he flew to a conference, and met up with Helen, an old colleague he occasionally traveled with.  They went to breakfast together, and started talking about their travel.} & \multirow{2}{\linewidth}{Greg said to Helen:} & ``I flew here. I took my cell phone on board with me.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Greg frequently travels by air, but hates carrying things around with him, and checks absolutely everything into the hold. $^{wonky}$ &  &  & ``I flew here. I got into business class.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{18} & Sandy usually cuts her own hair, although she has no training. $^{ordinary}$ & \multirow{2}{\linewidth}{Two days ago, after she gave herself another haircut, she went for a walk along her street.  She quickly ran into her ex, Patrick, and they stopped to catch up for a few minutes.} & \multirow{2}{\linewidth}{Sandy said to Patrick:} & ``I just cut my hair. I used scissors.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Sandy usually cuts her own hair, simply by taking a buzzer to it. $^{wonky}$ &  &  & ``I just cut my hair. I cut it a bit shorter than intended.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{19} & Henry often goes to art exhibitions, as there's an art museum a short walk from his place. $^{ordinary}$ & \multirow{2}{\linewidth}{Last week, after going to a new photography exhibition, he encountered his friend Max on his way home.  They paused on the street and chatted for a while.} & \multirow{2}{\linewidth}{Henry said to Max:} & ``I just went to the new photo exhibit. I looked at the photographs.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Henry often goes to art exhibitions, but only because his girlfriend drags him. $^{wonky}$ &  &  & ``I just went to the new photo exhibit. I decided to buy a photograph.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{20} & Helen works hard at her job, and enjoys the challenges she's given at work. $^{ordinary}$ & \multirow{2}{\linewidth}{Today, after driving her car to work as usual, she ran into her office-mate Peter while walking into the building.  They stopped briefly to say hello.} & \multirow{2}{\linewidth}{Helen said to Peter:} & ``I just parked my car. I locked it.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Helen works hard at her job, although she is incredibly scatterbrained. $^{wonky}$ &  &  & ``I just parked my car. One of my tail lights has gone out.'' $^{non-habitual}$ \\
\hline
\end{longtable}

\pagebreak

\begin{longtable}[c]{p{0.015\textwidth}||p{0.21\textwidth}|p{0.33\textwidth}|p{0.13\textwidth}|p{0.21\textwidth}}
&\centering\textsc{Common Ground}&\centering&&\multicolumn{1}{c}{\textsc{Utterance}} \\
\hline
\hline
\multirow{2}{*}{21} & Gary often orders pizza at work, from a famous pizzeria nearby. $^{ordinary}$ & \multirow{2}{\linewidth}{A few days ago, after he placed an order, his colleague Stephanie walked over to his cubicle to chat.} & \multirow{2}{\linewidth}{Gary said to Stephanie:} & ``I just ordered pizza. I picked the toppings.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Gary often orders pizza at work, but doesn't usually get to choose which type of pizza to get. $^{wonky}$ &  &  & ``I just ordered pizza. I used a gift certificate.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{22} & Julia always tries to wash the dishes after eating, to avoid annoying her roommates. $^{ordinary}$ & \multirow{2}{\linewidth}{A few days ago, she was getting ready to go out after doing the dishes.  She ran into her roommate Justin on her way out, and started talking to him.} & \multirow{2}{\linewidth}{Julia said to Justin:} & ``I just did the dishes. I rinsed them.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Julia always tries to wash the dishes after eating, but doesn't always bother to rinse them. $^{wonky}$ &  &  & ``I just did the dishes. I polished them.'' $^{non-habitual}$ \\
\hline\multirow{2}{*}{23} & Emma often borrows books from the library, as she doesn't have much spare cash to spend. $^{ordinary}$ & \multirow{2}{\linewidth}{Last week, after going to the library, she was heading home with several books, and ran into her best friend Tim on the street.  They stopped to quickly say hello.} & \multirow{2}{\linewidth}{Emma said to Tim:} & ``I just got some books at the library. I checked them out.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Emma often steals books from the library, as she doesn't have money to buy her own copies. $^{wonky}$ &  &  & ``I just got some books at the library. I looked at the library's exhibit.'' $^{non-habitual}$ \\
\hline
\multirow{2}{*}{24} & Logan recently started doing his own laundry, after moving out of his parents' house. $^{ordinary}$ & \multirow{2}{\linewidth}{Yesterday, after doing a load, he went to the living room to watch some TV.  Soon his roommate Sophia came home, and asked about his day while taking off her coat.} & \multirow{2}{\linewidth}{Logan said to Sophia:} & ``I just did the laundry. I used detergent.'' $^{habitual}$ \\\cline{2-2}\cline{5-5}
 & Logan recently started doing his own laundry, but can't get a handle even on the basics. $^{wonky}$ &  &  & ``I just did the laundry. I added some softener to the wash.'' $^{non-habitual}$ \\
 \hline
\end{longtable}
\addtocounter{table}{-1}